\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\PassOptionsToPackage{hyphens}{url}\usepackage[hidelinks]{hyperref}
\usepackage{siunitx}

\name{Marko Vejnovi\'{c}}
\address{1820 Sheridan Road \\ Evanston, Illinois 60201}
\address{(872)~$\cdot$~806~$\cdot$~4041 \\ markovejnovic2023@u.northwestern.edu}
\address{\url{www.markovejnovic.com} \\ \url{www.github.com/markovejnovic}}

\begin{document}

\begin{rSection}{Education}

{\bf Northwestern University} \hfill {\em September 2019 - Present} \\ 
Bachelors in Electrical Enginerering \\
Department of Electrical Engineering \\
Bachelors in Computer Science \\
Department of Computer Science

{\bf United World College Changshu China} \hfill {\em August 2017 - May 2019} \\
International Baccelaurate \\
Overall Percentage $82.2\%$

\end{rSection}

\begin{rSection}{Experience}

\begin{rSubsection}{UNAING}{Dec 2018 - Jan 2019}{Freelance Web Developer}{Banja Luka, Bosnia \& Herzegovina}
\item UNAING is an architectural company based in Banja Luka, Bosnia \& Herzegovina, founded in 2001 with the goal of building upon the culture of construction. UNAING does everything from architectonic design to creating urbanistic plans.
\item I worked at UNAING as a Web Developer. Working closely with the company, I designed a React-based website. The website is available at \url{www.unaing.com}.
\end{rSubsection}

\begin{rSubsection}{Zoran Kuva\'{c}}{August 2019 - September 2019}{Freelance Web Developer}{Banja Luka, Bosnia \& Herzegovina}
\item Zoran Kuva\'{c} is a professional classical guitar luthier. He required a website update.
\item I worked to rewrite Zoran Kuva\'{c}'s website in React. The website is available at \url{www.zorankuvac.com}.
\end{rSubsection}

\end{rSection}

\begin{rSection}{Projects}

\begin{rSubsection}{DIY Gibson Flying V Clone}{}{}{}
\item This project was a successful attempt at making a completely customized guitar by hand. All the elements on the guitar were made by hand, bar the tuning pegs and the electronics. Two AlNiCo pickups were wound by hand - one which produced a dull sound with swept mids, and one which produced a vibrant, bluesy and very vocal tone.
\end{rSubsection}

\begin{rSubsection}{Pickup Winder}{}{}{}
\item For the Flying V Project a Pickup Winding Machine was required. This was done by using an Arduino and an H-Bridge to control a motor driven shaft with an encoder. This enabled accurate measurements of the number of turns. The pickup wire was tightened manually.
\end{rSubsection}

\begin{rSubsection}{Ikap}{}{}{}
\item Ikap is a solution for managing the use of a kitchen in United World College Changshu China. The solution solves both time management of the kitchen and inventory tracking.
\end{rSubsection}

\begin{rSubsection}{USB Arduino-based Portable Oscilloscope}{}{}{}
\item The portable oscilloscope, awarded with the Gold Prize on Tesla Fest 2016, is a device which enables waveform analysis on the go by connecting it to an Android computer (tablet or phone), with up to $20\si{kHz}$ sampling rate.
\end{rSubsection}

\begin{rSubsection}{Automated Camera Slider}{}{}{}
\item One of the issues present with stop-motion animation is creating camera motion. The Automated Camera Slider is a cheap and robust solution for this problem. Employing both a manual mode and an automated mode (integrated with the de-facto industry standard Dragonframe), the Automated Camera Slider enables the animator to create camera motion effects with ease.
\end{rSubsection}

\end{rSection}

\begin{rSection}{Awards}

{\bf Portable Science Experiments Coiffer} \hfill {Gold Prize}\\
{\em 2014} \hfill {\em INOST 2014}

{\bf Arduino Camera Slider} \hfill {Silver Prize}\\
{\em 2015} \hfill {\em INOST 2015}

{\bf USB Arduino-based Portable Oscilloscope} \hfill {Gold Prize}\\
{\em 2016} \hfill {\em Tesla Fest 2016}

{\bf System for Organizing Small Aeroclubs} \hfill {Silver Prize}\\
{\em 2017} \hfill {\em INOST 2017}

\end{rSection}

\begin{rSection}{Research}

\begin{rSubsection}{The Frequency Response of the MXR Microamp Amplifier}{July 2018}{}{}
\item The MXR Microamp amplifier is used as a guitar pedal which boosts the input signal and must have a flat frequency response. The goal was to identify whether this is so.
\item Paper available at: \url{https://github.com/markovejnovic/freq-response-microamp/raw/master/tex/freq-response.pdf}
\end{rSubsection}

\begin{rSubsection}{The Effect of Pickup Position on the Response of an Electric Guitar}{October 2018}{}{}
\item The goal of this research paper was to investigate the effect of pickup position on the frequency response of its harmonics.
\item The goal was not successfully achieved either because of poor harmonic identification, inconsistent waveform deterioration, inconsistencies when plucking the string.
\item Paper available at: \url{https://github.com/markovejnovic/Pickup-Position-Effects/raw/master/tex/relation-pickup-distance.pdf}
\end{rSubsection}

\end{rSection}

\begin{rSection}{Technical Abilities}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Drawing, Modelling \& Analysis 	& AutoCAD, Solidworks, EagleCAD \\
Office Software 			& Microsoft Office \\
General Languages			& C, C++, C\#, Objective-C, Java, Javascript, Python, PHP, \\
					& Kotlin, Bash, Powershell \\
Data Processing			& Numpy, Scipy, TensorFlow, Matlab \\
Web Technologies 			&  HTML, CSS, JS, Typescript, React, Flask, PHP, Node.js,\\
					& REST, HTTP, Sockets \\
Mobile Technologies 		& Android, iOS, watchOS \\
Database Technologies		& MySQL, PostgreSQL, SQLite \\
Data Description Technologies 	& XML, JSON \\
Typesetting Systems 		& \LaTeX \\
Embedded Systems 		& Arduino, AVR, PIC (mikroC) \\
System Administration 		& *nix System Administration \\
Design and Film Technologies 	& Photoshop, Illustrator, Audition, Premiere Pro \\
Desktop Technologies 		& GTK, Qt, Winforms, MFC, Win32, Swing \\
Tools 					& Git, Vim
\end{tabular}

\end{rSection}

\end{document}
